An Algebraic Theory of File Synchronization

### 2016-01-03 2015/ordering.tex
Fixed typos
Completed proof for equivalence is reordering

\begin{mylem}\label{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
but $\nn\neq\parent(n)$, then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by repapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

@@

As a specific case, we can regard a simple sequence of commands $S$
as a set and determine its $\orderset{S}$.
An important property of simple sequences is that
all of their valid orderings are equivalent,
and all equivalent sequences are mere reorderings:

\begin{mylem}\label{simple_reorder_equiv}
For any simple sequence $S\nequiv\cbrk$,
$\forall T: T\equiv S \Leftrightarrow T\in\orderset{S}$.
\end{mylem}
\begin{proof}
First, as $S$ only has at most one command on each node,
any sequence in $\orderset{S}$ either breaks a filesystem,
or it leaves it in the same state as $S$.

@@

From these we know that all sequences in $\orderset{S}$
are equivalent, and that any sequence $T$ outside it
necessarily breaks all filesystems.

Therefore if $S\nequiv\cbrk$ then $S\in\orderset{S}$,
and $S$ cannot be equivalent to any sequence of the same commands
not in $\orderset{S}$.
\end{proof}

>>>>

\begin{mylem}\label{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$
but $\nn\neq\parent(n)$, then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

@@

As a specific case, we can regard a simple sequence of commands $S$
as a set and determine its $\orderset{S}$.
An important property of simple sequences is that
all of their valid orderings are equivalent,
and all equivalent sequences are mere reorderings.
To prove this, first we prove the following:

\begin{mylem}\label{equiv_simple_same_commands}
If two simple sequences $A$ and $B$ are equivalent
and do not break all filesystems ($A\equiv B\nequiv\cbrk$),
then they must contain the same commands.
\end{mylem}
\begin{proof}
We use an inverse proof. Let $A$ and $B$ simple sequences
such that $A\equiv B\nequiv\cbrk$,
and $\FS$ be a filesystem that they do not break.

We also assume that they do not contain the same sequences.
Without loss of generality, we can assume
that $A$
contains $\cxynv$, and $B$ either contains a different command
$\czwnv$ on $n$, or no command on $n$ at all.
As $A$ is simple, we know that $\cxynv$ is not an assertion command,
and therefore $X\neq Y$ and $\FS(n)\neq\valvy$ as it has type $X$.
If so, then if $B$ has no command on $n$, then $B\aFS(n)=\FS(n)$ and
$A$ and $B$ cannot be equivalent.
Otherwise we know that $Z=X$ as $B$ does not break $\FS$ either,
and that $\valvw=\valvy$ and therefore $W=Y$ as $B\aFS(n)$ must
be $\valvy$ and $B$ only has one command on $n$.
However, then $\czwnv=\cxynv$, which is a contradiction.
\end{proof}

\begin{mylem}\label{simple_reorder_equiv}
For all simple sequences $T$ and $S\nequiv\cbrk$,
$T\equiv S \Leftrightarrow T\in\orderset{S}$.
\end{mylem}
\begin{proof}
First, as $S$ only has at most one command on each node,
any sequence in $\orderset{S}$ either breaks a filesystem,
or it leaves it in the same state as $S$.

@@

From these we know that all sequences in $\orderset{S}$
are equivalent, and that any sequence of the same commands outside it
necessarily breaks all filesystems.
We also know $S\in\orderset{S}$ as $S\nequiv\cbrk$
and therefore $T\in\orderset{S} \Rightarrow T\equiv S$.

From \cref{equiv_simple_same_commands} we know that 
if $T\equiv S$, then $T$ contains the same commands as $S$,
from which we see
that $T\equiv S\Rightarrow T\in\orderset{S}$.
\end{proof}
